---
title: "UNIT 1 ASSIGNMENT"
author: "SANTHOSH S"
date: "26.09.2022"
output: html_document
---

### ASSIGNMENT QUESTIONS AND SOLUTIONS

#### Introduction Exercises:  

library(ggplot2)

```{r}
```
question  1

What happens if you make a scatterplot of class versus drv? Why is the plot not useful?
```{r}
 ggplot(mpg, aes(x=class,y=drv))+
          geom_point()

```

question 2

What’s gone wrong with this code? Why are the points not blue?
 ggplot(data = mpg) + 
   geom_point(aes(x = displ,y = hwy, color = "blue"))

ans:the points are not blue because the perameter color is included with aesthetic. if color is placed outside displays the points in blue color
```{r}
ggplot(data = mpg) + 
   geom_point(aes(x = displ,y = hwy), color = "blue")

```

question 3

a) What happens if you map a aesthetic to something other than a variable name,

like aes(colour = displ<5)?

```{r}

ggplot(data=mpg)+
    geom_point(mapping = aes(x=displ,y=hwy,color=displ<5))

```
b) What does the stroke aesthetic do? What shapes does it work with?

```{r}
ggplot(data=mpg)+
    geom_point(aes(x=displ,y=hwy,stroke=3))

```

stroke is used to adjust the border size for shapes. it work with points(geom_point)shape.

question 4

Read? Facet_wrap. What does nrow do? What does ncol do? What other options
control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol variables?


The arguments nrow (ncol) determines the number of rows (columns) to use when laying out the facets. It is necessary since facet_wrap() only facets on one variable.

The nrow and ncol arguments are unnecessary for facet_grid() since the number of unique values of the variables specified in the function determines the number of rows and columns.


question 5

a) What plots does the following code make? What does . do?

```{r}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(drv ~ .)

```
```{r}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(. ~ cyl)

```

b) When using facet_grid() you should usually put the variable with more unique
levels in the columns. Why?

There will be more space for columns if the plot is laid out horizontally (landscape)

question 6

What geom would you use to draw a line chart? A boxplot? A histogram? An area
chart?


ans:
  line_chart:geom_line()
  box_plot:geom_boxplot()
  histogram:geom_histogram()
  area_chart:geom_area()
  
question 7

Will these two graphs look different? Why/why not?

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
geom_point() +
geom_smooth()

```

```{r}
ggplot() +
geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) +
geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))

```
ans: no,the two graphs looks similar.because both geom_point() and geom_smooth()
use same data and mappings

question 8

What does geom_col() do? How is different to geom_bar()?

ans:
  The geom_col() function has different default stat than geom_bar(). The default stat of geom_col() is stat_identity(), which leaves the data as is. The geom_col() function expects that the data contains x values and y values which represent the bar height.

The default stat of geom_bar() is stat_count(). The geom_bar() function only expects an x variable. The stat, stat_count(), preprocesses input data by counting the number of observations for each value of x. The y aesthetic uses the values of these counts.


  question 9
  
  What is the default geom associated with stat_summary()? How could you rewrite the previous plot to use that geom function instead of the stat function?
  
  


question 10

What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?

```{r}
ggplot(data = mpg, mapping =aes(x =cty, y =hwy)) +
geom_point() +
geom_abline() +
coord_fixed()

```



